\documentclass{article} 
\usepackage{fullpage}

\begin{document}

\section{Overview}

\paragraph{} You will play a game similar to I, Spy with the robot. You will go first, describing an object on the table to the robot. The robot will point to objects and ask whether it has selected the right one until it guesses correctly. Then the robot will attempt to describe an object to you, and you will pick up objects to indicate your guess until you select correctly.

\paragraph{} After picking up an object on the table, be sure to place it back down on the `x'-marker from which you took it.

\paragraph{} When speaking to the robot, say oyur words loudly and clearly, but don't over-enunciate. If you can't understand the robot, ask it to repeat itself by saying ``Can you repeat that?'' or ``What did you say''?

\paragraph{} You'll play two games of I, Spy with the robot. During the intermission between, the experimenter will need to set up a new set of objects. During this time, you may be asked to step out of the room.

\section{Your Turn}

\paragraph{} On your turn, pick an object in your mind. As in I, Spy, you want to describe properties of this object rather than stating exactly what it is (e.g. ``something black and rectangular'' as opposed to ``a whiteboard eraser''). In addition to looking at the objects, the robot has had the opportunity to explore these objects in non-visual ways, such as picking them up, pushing, and squeezing them. You should feel free to explore the object you want to describe by picking it up and examining it physically before offering your description. Don't worry---the robot won't cheat by remembering which one you were exploring.

\paragraph{} Say your description out loud when you're ready. The robot will make guesses by extending its arm over the object it thinks you described and ask you to confirm or deny whether it guessed correctly. This process will repeat until it guesses correctly.

\section {Robot's Turn}

\paragraph{} On the robot's turn, it will pick an object and try to describe that object to you. Again, you should feel free to explore the objects on the table physically.

\paragraph{} When you're ready to start guessing, move your hands away from the objects and say ``okay''. This lets the robot know the next object you pick up is your guess. Reach out and pick up the object you think the robot is describing, then put it back down when the robot tells you whether or not this was the correct object. If you're wrong, pick up a different object to guess again. 

\end{document}
